\thispagestyle{empty}
\begin{center}
%\vspace{1.2in}
\vspace*{11pt}
%{\Huge \bf DISSEMINATION OF WORK}  
\end{center}
\vspace{0.05in}
{\bf JOURNAL PAPERS}
\begin{enumerate}
\item{{\bf Dynamically balanced ascending and descending gaits of a two-legged robot}}\\
           {\it International Journal of Humanoid Robotics}, (2007) 4(4) 717-751.
\item{{\bf Online dynamically balanced ascending and descending gait generations of a biped robot using soft computing}}\\
           {\it International Journal of Humanoid Robotics}, (2007) 4(4) 777-814.   
\item{{\bf Soft computing-based gait planners for a dynamically balanced biped robot negotiating sloping surfaces}}\\
	   {\it Applied Soft Computing}, (in press).
\item{{\bf Dynamically balanced gaits of a two-legged robot on sloping surface}}\\
	   {\it Robotica}, (under review).
\item{{\bf Optimal gait generations of a two-legged robot on rough terrains using soft computing}}\\
	   {\it IEEE Syatems Man and Cybernetics-Part A: Systems and Humans}, (under review).
\item{{\bf Dynamically balanced optimal gaits of a ditch-crossing biped robot}}\\
	   {\it Robotics and Autonomous Syatems}, (under review).
\item{{\bf Neural Network-based inverse dynamics learned gait planner for a two-leeged robot on uneven terrains}}\\
	   {\it INternational Journal of Robotic Research}, (under review).
\end{enumerate}
\newpage
{\bf CONFERENCE PAPERS}
\begin{enumerate}
\item{{\bf Ditch-crossing gait generation of a two-legged robot using soft computing}}\\
	   {\it International Conference on Embeded Systems, Mobile Communication and Computing}, August 11-14, 2008,  
	   Mysore, India, (Accepted).
%%%%%	1 more papers be added	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	   	   
\end{enumerate}
\newpage

