\chapter{Auxiliary Format}
\label{chap:Auxfrmt}
This section provides general information regarding the format of Thesis for NIT Agartala. The users of \LaTeXe will be able to generate the formats, mentioned here, with help of the latex file \textbf{thesis-NITA.tex} and other \textbf{tex files} available in the folder \verb+Thesis-NITA-2018+ at the institute \textbf{MIS home page}. The information provided are worth for users of \textbf{MS Word}. Samples of various formats for MS word users are provided in the Appendix.
\section{Binding}
The evaluation copies of the thesis/dissertation/report may be spiral bound or soft bound. The final hard bound copies to be submitted after the viva-voce examination. They have to be hard-bounded with the following color specifications:
\begin{itemize}
	\item Ph.D. Thesis  Dark Blue  [RGB (0,0,139)]
	\item M.Tech./ MT(Engg Physics) Dissertation Black
	\item B.Tech./B.T.(Engg Physics)/BSMS/M.Sc. Project Report Saddle brown[RGB (139,69,19)]
\end{itemize}

\section{Front and Side Covers}
The front cover shall contain the following details:
\begin{itemize}
	\item Full title of thesis in \textbf{18} to \textbf{22} point's size font (bold) properly centered and positioned at a distance of \textbf{25 cm} from the top.
	\item Institute emblem of size 2” height should be placed at the centre of the front cover page.
	\item Name of candidate (in Italic) along with the name of Department, Institute, …… Year is in \textbf{12} to \textbf{16-point} size, bold shall be placed at a distance of 25 cm from the bottom.
\end{itemize}
\par \LaTeX users need to edit the \textbf{cover.tex}.
\par The side cover shall contain the following details:
•	Name of degree along with name of thesis and candidates name is to be provided at the closed side of the bounded book. \LaTeX users need to edit the \textbf{side.tex}.
Following Sample copies are appended 
\begin{itemize}
	\item{\bf{Front Cover:}} \textbf{Specimen A} 
	\item{\bf{Side Cover:}}  \textbf{Specimen B}
\end{itemize}
  
\subsection{Lettering in Front Cover and Side Cover}
All lettering shall be embossed in silver.
\section{Blank Sheets}
In addition to the white sheets (binding requirement) two white sheets shall be put at the beginning and the end of the thesis.
\section {Title Sheet}
This shall be the first printed page of the thesis and shall contain the submission statement: the Thesis/Dissertation/project Report submitted in partial fulfillment of the requirements of the Degree, Ph.D. /M.Tech./B.Tech./M.Sc., the name and Roll No. of the candidate, name(s) of the Supervisor and Co-supervisor (s) (if any), Department, Institute and year of submission.
\par A sample copy of the 'Title Sheet' is appended \textbf{Specimen C}. \LaTeX users need to edit the \textbf{title.tex}

\section{Dedication Sheet}
The dedication sheet and the thought (or Idea) sheet are auxiliary pages. If the candidate so desires (s)he may dedicate his/her thesis, which statement shall follow the title page. If included, this shall form the page i of the auxiliary sheets,  but shall not have a page number. If the candidate so desires (s)he may incorporate one thought (or idea) sheet which follow the dedication sheet. \LaTeX users need to edit the \textbf{dedi.tex}

\section{Approval Sheet}
In the absence of a dedication sheet this will form the first page and in that case shall not have a page number. Otherwise, this will bear the number two in Roman lower case “ii” at the center of the footer. \LaTeX users need to edit the \textbf{approval.tex}.

The top line shall be:
\begin{enumerate}
	\item Thesis Approval for Ph.D
	\item Dissertation Approval for M.Tech\textbackslash MCA\textbackslash MBA
	\item Report Approval for B.Tech\textbackslash B.S.\textbackslash M.Sc. 
\end{enumerate}

The \textbf{Approval Sheets} are to be \textbf{included only} in the hard bound copies which are submitted after the \textbf{successful} Ph.D. viva-voce examination.
\par A sample copy of the Approval Sheet is appended in \textbf{Specimen D}
\section{Declaration of Academic Honesty and Integrity}

\par A declaration of Academic honesty and integrity is required to be included along with every thesis/dissertation/report after the approval sheet. The format of this declaration is appended in \textbf{Specimen E}. \LaTeX users need to edit the \textbf{declaration.tex}.
\section{Certificate}
A certificate is obtained from supervisor/supervisor (s) is to be enclosed. The format of this certificate is given in \textbf{Specimen F} attached. \LaTeX users need to edit the \textbf{cert.tex}.
\section{Acknowledgment and Curriculum Vitae}
The Candidate should  one or two pages \textbf{Acknowledgment} and one page \textbf{Curriculum Vitae}. Curriculum Vitae is to be given at the last of the thesis after Appendices. \LaTeX users need to edit the \textbf{acknowledgment.tex} \& \LaTeX users need to edit the \textbf{cv.tex}..
\section{Contents}
The contents shall enlist the titles of the chapters, section and subsection using decimal notation, as in the text, with corresponding page numbers against them, flushed to the right. The format of the contents is given in \textbf{Specimen G} attached. For \LaTeX user \textbf{Contents} will be auto generated.
\section{List of Figures and List of Tables}
Two separate lists of Figure captions and Table titles along with their numbers and corresponding page numbers against them shall follow the Contents. After that the list of symbols as used in the thesis is to be given. For \LaTeX users \textbf{List of Figures} \& \textbf{List of Tables} will be auto generated.
\section{Symbols, Abbreviation and Notation}
A complete and comprehensive list of all symbols, abbreviations and notations including Greek alphabets with subscripts and superscripts shall be provided after the list of   figures and tables. (As far as possible, generally accepted symbols and notation should be used). \LaTeX users need to edit the \textbf{nomen.tex}.
\section{Abstract}
A M Tech thesis should contain an abstract not exceeding 300 words (about one page), and a Ph.D. thesis should contain an abstract/synopsis not exceeding 500 words (about one and half pages) in \textbf{single spacing}. The abstract shall highlight the important features of the thesis/ dissertation/report and shall correspond to the electronic version to be submitted to the Library for inclusion in the website. The Abstract in the thesis, however, shall have two more parts, namely, the layout of the thesis giving a brief chapter wise description of the work and the key words. \LaTeX users need to edit the \textbf{abst.tex}.
\section{Units}
The units used in the thesis should be SI units.
\section{Pagination}
An auxiliary page from dedication (if any) to abbreviations shall be numbered using Roman numerals in lower case.

Page numbers for the body of the thesis should be in Arabic numerals and should be centered at the bottom of the pages. The pagination should start with the first page of Chapter 1 and should continue throughout the text (including tables, figures, and appendices).

